Effects of Uncertainty in Heterogeneous Models

### 2017-01-24 presentation/presentation.tex
4th section
Change titles
Change policy change
Changing Yannics title
remove the
of KS added

\section{Welfare analysis of unemployment benefits}
\subsection{}
\begin{frame}{Welfare Analysis}
  \begin{itemize}
  \item {
  Which variable should we look at if we want to say consumers are better off? Output? Consumption?
  }
  \item {
  We want to measure somehow whether consumer welfare increased or not.
  }
  \item {
  But how to measure welfare? Can we compare the utility levels of consumers? And whose utility should we compare in a heterogeneous agent framework?
  }
  \end{itemize}
\end{frame}

@@

\section{Aggregate uncertainty}
\subsection{The cost of the business cycle}

@@

\subsection{Numerical problems}

\begin{frame}{Another application}{Transition between two steady states for 10k individuals}
\centering{\includegraphics[width=12cm,height=6cm,keepaspectratio]{fig3}}
\end{frame}

\begin{frame}{Another application}{Transition between two steady states for 100k individuals}
\centering{\includegraphics[width=12cm,height=6cm,keepaspectratio]{fig4}}
\end{frame}

\begin{frame}{Another application}{Transition between two steady states for histogram method}
\centering{\includegraphics[width=12cm,height=6cm,keepaspectratio]{fig5}}
\end{frame}

>>>>

\section{Optimal unemployment benefit}
\subsection{}
\begin{frame}{Welfare Analysis}
  \begin{itemize}
  \item {
  Which variable should we look at if we want to say consumers are better off? Output? Consumption?
  }
  \item {
  We want to measure somehow whether consumer welfare increased or not.
  }
  \item {
  But how to measure welfare? Can we compare the utility levels of consumers? And whose utility should we compare in a heterogeneous agent framework?
  }
  \end{itemize}
\end{frame}

@@

\section{Business cycle costs}
\subsection{}

@@

\section{Numerical problems}
\subsection{}
\begin{frame}{Another application of Krussel - Smith}{Transition between two steady states for 10k individuals}
\centering{\includegraphics[width=12cm,height=6cm,keepaspectratio]{fig3}}
\end{frame}

\begin{frame}{Another application of Krussel - Smith}{Transition between two steady states for 100k individuals}
\centering{\includegraphics[width=12cm,height=6cm,keepaspectratio]{fig4}}
\end{frame}

\begin{frame}{Another application of Krussel - Smith}{Transition between two steady states for histogram method}
\centering{\includegraphics[width=12cm,height=6cm,keepaspectratio]{fig5}}
\end{frame}
